Cheat Sheet for PFPL

### 2016-08-10 pfpl/draftcheatsheet.tex
Bring up to chapter 34
Add assign and reference

81 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
\end{tabular}

>>>>

81& 308 & $a := e$ & Colon equals & Assign & Assign $e$ to $a$\\
82 & 308 & $*a$ & Star & Reference & Get the value of $a$\\
82 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
83 & 314 & $ m \thicksim \tau$ & Dotted tilde & Dotted tilde & Command $m$ returns a value of type $\tau$\\
\end{tabular}
